A zero-knowledge protocol tries to convince a verifier about the truth of a
statement without revealing any additional information. These include proving the correctness of
transactions in cryptocurrencies such as \cite{zerocash} or validating sensitive web browser data reported during
telemetry \cite{prio, MozillaPrio}. Still in the dream of a decentralized world, there are
multiple co-opetitive entities, i.e., collaborating but mutually distrusting entities interacting with each other to obtain insights
and maximize their goals. We envisage applications of zero-knowledge
proofs to enable these mutually
distrusting entities to prove a claim on their joint data. In this setting, the traditional zero-knowledge protocols are restrictive since they require
a single prover to have the entire witness needed to generate the proof. 

In this work, we study the general setting of \textit{distributed prover zero-knowledge protocols} ($\DPZK$) where multiple co-opetitive entities, each possessing its own secret data, want to prove to a verifier that their secret data together satisfy a predicate of common interest. This is to be done without revealing any information
about their sensitive data to each other or to the verifier. 

Formally, we have multiple provers $\prover_1, \ldots, \prover_{\Num}$
respectively possessing witnesses $\wit_1, \ldots, \wit_{\Num}$. For a predicate $C$ the provers wish to prove to a verifier that $C(\wit_1,\cdots,\wit_{\Num}) = 1$.  
A natural solution for distributed
proof generation is to start with the prover algorithm of a single prover
protocol and run this algorithm between multiple provers using multi-party computation (MPC). This generic construction was discussed by Pedersen~\cite{Ped92}. 
However, the generic construction is unlikely to be efficient in practice. Known constructions of efficient zero-knowledge proofs involve
expensive computation (e.g. $\fft$) over complex mathematical structures such as fields, groups and elliptic curves, which are expensive when expressed
as an arithmetic circuit. Running multiparty computation over such circuits with several parties will be prohibitive. 
To get around the inefficiency of a generic construction, some prior works have proposed efficient distributed proof generation for 
restricted class of computations.
These include simple predicates involved in threshold signatures \cite{DDS}, some sigma protocols \cite{EfficientTZ}, 
combined range proofs \cite{bulletproofs}. Distributed proof generation for more general computation has been considered in \cite{trinocchio}, but under
weaker trust model involving a trusted setup and majority of the parties
being honest \cite{trinocchio}. The goal of this paper is to enable DPZK for general computation without requiring trusted setup or honest majority. 
We summarize our contributions below.

\paragraph*{Our contributions}
\begin{itemize}
	%----------
	\item We provide a formal definition of distributed prover zero-knowledge ($\DPZK$) in the real-ideal world paradigm. Furthermore, we identify and motivate relevant efficiency parameters to measure the efficiency of a $\DPZK$ protocol. 
	%----------
	\item \ADDED{We present a compiler that takes any IOP-based zero-knowledge protocol and converts it to an ``MPC-friendly'' zero-knowledge protocol 
	which can then be used to obtain a $\DPZK$ protocol.}
	%----------
	\item We illustrate the application of our compiler for two single-oracle IOPs, which is the preferred setting for our compiler.
	We obtain the protocol \textsf{D-Ligero} by using our compiler with the Ligero protocol from \cite{ligero}. Building upon the techniques
	used in Ligero, we construct a new single-oracle IOP which we call \name. The protocol \name\ admits smaller proof sizes
	than Ligero while ensuring efficient verification. Moreover we show that \name\ can also be efficiently compiled to yeild a DPZK protocol, 
	which we call \dpname. The zero knowledge protocols are described as interactive protocols secure against honest verifiers. Using standard
	transforms such as \cite{FS86, BCS16}, they can be used to obtain succint non-interactive arguments of knowledge (SNARGs), 
	which are secure against malicious verifiers in the Random Oracle model.
	%----------
\end{itemize}
Before providing a detailed overview of our work, we discuss potential real-world applications where distributed proof generation can be useful. 


\input{mwanonymous}